Linking hypothesis and number of response options modulate inferred scalar implicature rate

### 2018-05-10 writeup.Rmd
added word count, linguistic exmpales, and conflict of interest statement

  - name          : "Masoud Jasbi"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Margaret Jacks Hall, Building 460 Rm. 127, Stanford, CA, 94305-2150"
    email         : "masoudj@stanford.edu"
  - name          : "Brandon Waldon"
    affiliation   : "1"
  - name          : "Judith Degen"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Stanford University, Department of Linguistics"
author_note: |
  XXX Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  The past 15 years have seen increasing experimental investigations of core pragmatic questions in the ever more active and lively field of experimental pragmatics. Within experimental pragmatics, many of the core questions have relied on the operationalization of the theoretical notion of 'implicature rate'. Implicature rate based results have informed the work on acquisition, online processing, and scalar diversity, inter alia. Despite its theoretical importance. Implicature rate has  typically been quantified as the proportion of 'pragmatic' judgments in two-alternative forced choice truth value judgment tasks. Despite its theoretical importance, this linking hypothesis from implicature rate to behavioral responses has never been extensively tested. Here we show that two factors dramatically affect the 'implicature rate' inferred from truth value judgment tasks: a) the number of responses provided to participants; and b) the linking hypothesis about what constitutes a 'pragmatic' judgment. We argue that it is time for the field of experimental pragmatics to engage more seriously with its foundational assumptions about how theoretical notions map onto behaviorally measurable quantities, and present a sketch of an alternative linking hypothesis that derives behavior in truth value judgment tasks from probabilistic utterance expectations.
keywords          : "scalar implicature; methodology; linking hypothesis; experimental pragmatics; truth value judgment task"
wordcount         : "X"
bibliography      : ["r-references.bib"]
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
class             : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: inline
---

@@

1. 
  + *Utterance:* Some of her pets are cats.
  + *Implicature:* Some, but not all, of her pets are cats.
  + *Scale:* <all, some>

2. 
  + *Utterance:* She owns a cat or a dog.
  + *Implicature:* She owns a cat or a dog, but not both.
  + *Scale:* <and, or>

@@

    $P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s)$

    $P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) $

    $P_{L_0}(s | u) \propto [[u]](s) * P_w(s)$

>>>>

  - name          : "Masoud Jasbi"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Margaret Jacks Hall, Building 460 Rm. 127, Stanford, CA, 94305-2150"
    email         : "masoudj@stanford.edu"
  - name          : "Brandon Waldon"
    affiliation   : "1"
  - name          : "Judith Degen"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Stanford University, Department of Linguistics"
author_note: |
  The authors declare that they have no affiliations with, or involvement in any organization or entity with any financial interest, or non-financial interest in the subject matter or materials discussed in this manuscript. 
abstract: |
  The past 15 years have seen increasing experimental investigations of core pragmatic questions in the ever more active and lively field of experimental pragmatics. Within experimental pragmatics, many of the core questions have relied on the operationalization of the theoretical notion of 'implicature rate'. Implicature rate based results have informed the work on acquisition, online processing, and scalar diversity, inter alia. Despite its theoretical importance. Implicature rate has  typically been quantified as the proportion of 'pragmatic' judgments in two-alternative forced choice truth value judgment tasks. Despite its theoretical importance, this linking hypothesis from implicature rate to behavioral responses has never been extensively tested. Here we show that two factors dramatically affect the 'implicature rate' inferred from truth value judgment tasks: a) the number of responses provided to participants; and b) the linking hypothesis about what constitutes a 'pragmatic' judgment. We argue that it is time for the field of experimental pragmatics to engage more seriously with its foundational assumptions about how theoretical notions map onto behaviorally measurable quantities, and present a sketch of an alternative linking hypothesis that derives behavior in truth value judgment tasks from probabilistic utterance expectations.
keywords          : "scalar implicature; methodology; linking hypothesis; experimental pragmatics; truth value judgment task"
wordcount         : "9037"
bibliography      : ["r-references.bib"]
figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
class             : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: inline
---

@@

(1) Some of her pets are cats.

*Implicature:* Some, but not all, of her pets are cats.

*Scale:* $<$all, some$>$

(2) She owns a cat or a dog.

*Implicature:* She owns a cat or a dog, but not both.

*Scale:* $<$and, or$>$

@@

$$

    P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s) \\

    P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) \\

    P_{L_0}(s | u) \propto [[u]](s) * P_w(s)

$$

### 2018-05-10 writeup.tex
added word count, linguistic exmpales, and conflict of interest statement

\documentclass[floatsintext,man]{apa6}

@@

@@

  \affiliation{
    \vspace{0.5cm}
          \textsuperscript{1} Stanford University  }

  \authornote{
    XXX Add complete departmental affiliations for each author here. Each
    new line herein must be indented, like this line. Enter author note
    here.

    Correspondence concerning this article should be addressed to Masoud
    Jasbi, XXX Postal address. E-mail: XXX
    \href{mailto:my@email.com}{\nolinkurl{my@email.com}}
  }

@@

    \indent Word count: X
  }

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
\end{enumerate}

\begin{itemize}
\tightlist
\item
  \emph{Utterance:} Some of her pets are cats.
\item
  \emph{Implicature:} Some, but not all, of her pets are cats.
\item
  \emph{Scale:} 
\end{itemize}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\item
\end{enumerate}

\begin{itemize}
\tightlist
\item
  \emph{Utterance:} She owns a cat or a dog.
\item
  \emph{Implicature:} She owns a cat or a dog, but not both.
\item
  \emph{Scale:} 
\end{itemize}

@@

\begin{verbatim}
$P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s)$

$P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) $

$P_{L_0}(s | u) \propto [[u]](s) * P_w(s)$
\end{verbatim}

>>>>

\documentclass[man]{apa6}

@@

  \usepackage{ifthen} % Only add declarations when endfloat package is loaded
  \ifthenelse{\equal{\string man}{\string man}}{%
   \DeclareDelayedFloatFlavor{ThreePartTable}{table} % Make endfloat play with longtable
   % \DeclareDelayedFloatFlavor{ltable}{table} % Make endfloat play with lscape
   \DeclareDelayedFloatFlavor{lltable}{table} % Make endfloat play with lscape & longtable
  }{}%

@@

  \affiliation{
    \vspace{0.5cm}
          \textsuperscript{1} Stanford University, Department of Linguistics  }

  \authornote{
    The authors declare that they have no affiliations with, or involvement
    in any organization or entity with any financial interest, or
    non-financial interest in the subject matter or materials discussed in
    this manuscript.

    Correspondence concerning this article should be addressed to Masoud
    Jasbi, Margaret Jacks Hall, Building 460 Rm. 127, Stanford, CA,
    94305-2150. E-mail:
    \href{mailto:masoudj@stanford.edu}{\nolinkurl{masoudj@stanford.edu}}
  }

@@

    \indent Word count: 9037
  }

@@

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  Some of her pets are cats.
\end{enumerate}

\emph{Implicature:} Some, but not all, of her pets are cats.

\emph{Scale:} \(<\)all, some\(>\)

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  She owns a cat or a dog.
\end{enumerate}

\emph{Implicature:} She owns a cat or a dog, but not both.

\emph{Scale:} \(<\)and, or\(>\)

@@

\$\$

\begin{verbatim}
P_{L_1}(s | u) \propto P_{S_1}(u | s) * P_w(s) \\

P_{S_1}(u | s) \propto exp(\alpha(log(L_0(s | u)) - C(u))) \\

P_{L_0}(s | u) \propto [[u]](s) * P_w(s)
\end{verbatim}

\$\$
